---
title: "Module 3 Project 3: Presentation or Website Visualization Assignment"
subtitle: "INSH 5302 -  Information Design & Visual Analytics"
author: "ENTER YOUR NAME HERE"
date: "Apr 7, 2024"
output:
  html_document:
    code_download: true
    fig_caption: yes
    theme: lumen
    toc: yes
    toc_depth: 2
    df_print: kable
    toc_float:
      collapsed: no
---

```{r, message=FALSE}
# Required packages for our course. Do not delete.
library(tidyverse)
library(mosaic)
```

# Big-picture

## Research Question

*What is the question you hope to answer with your data visualization?*

> DELETE THE QUESTION ABOVE AND PROVIDE YOUR ANSWER HERE

* * *

# Data

## Description of data

*Please give a very short description of the data set along with it's original source. If it is part of a package, please indicate that.*

> DELETE THE PROMPT ABOVE AND PROVIDE YOUR ANSWER HERE

## Load data into R

*Include the code to load your data here. Using the head() function, show the first 10 rows of data. *

```{r, message = FALSE, warning = FALSE}

```

* * *

# Variables

*Using the names() function, show the names of all the columns (i.e. potential variables) in your data set. Delete this when complete.*
```{r, message = FALSE, warning = FALSE}

```

The variables I used in my data visualization design are:

1. Variable 1
2. Variable 2
3. Variable 3
4. Variable 4
5. Variable 5

* * *

# Data Analysis

## Summary Statistics

*Using the favstats() function, calculate the necessary statistics you used to create your data visualization. Delete this when complete.*
```{r, message = FALSE, warning = FALSE}

```

> Provide the high-level insights you used to craft your data visualization design.

## Additional Analyses

*If you conducted any other analyses of your data set to gather the data in your project, use this section to conduct your research. Delete this when complete.*
```{r, message = FALSE, warning = FALSE}

```

* * *

# Interactive Presentation or Website Visualiztion

*Module 3's Project allows students to choose ONE OPTION among the two options provided below. You should denote which ONE of the two options you plan to pursue and provide a brief overview of your vision for the project. Delete the other options that you will not be pursuing.*

## Option 1 | Interactive Canva Presentation
Students will use Canva to create an interactive presentation that showcases their data findings and creates a cohesive, one-stop hub for information regarding their topics. Students must include a minimum of 5 pages of analysis, 1 page for their home, and 1 page for references/overview. 

### Link to Canva Presentation Dashboard

**Embed your Canva presentation here. Don't forget to add in `data-external="1"` at the end of your `<iframe>` or else R-Markdown will not display properly. Delete this instruction once your presentation is embedded.**

### Descriptions of Canva Pages (Excluding the Home Page and Reference Page)

For each page, you should provide detailed reflection on the data visualization you used and how it helps to answer your over arching research question. 

#### Canva Page 1

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Canva Page 2

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Canva Page 3

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Canva Page 4

> Provide a summary of what this visualization shows and how it helps to answer your research question.

#### Canva Page 5

> Provide a summary of what this visualization shows and how it helps to answer your research question.

## Option 2 | Interactive Website
Students will create a website that present their data findings and topic in a website where users can engage with their platform. Students must include a minimum of 5 pages of analysis, 1 page for their home, and 1 page for references/overview. 

- Website Softwares Students are Allowed to Use:
  + Canva (Free!),
  + DreamWeaver (if students have web hosting), 
  + SharePoint (Free!), or 
  + Google Sites (Free!)

### Descriptions of Website Pages (Excluding the Home Page and Reference Page)

For each page, you should provide detailed reflection on the data visualization you used and how it helps to answer your over arching research question. 

#### Website Page 1

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Website Page 2

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Website Page 3

> Provide a summary of what this visualization shows and how it helps to answer your research question. 

#### Website Page 4

> Provide a summary of what this visualization shows and how it helps to answer your research question.

#### Website Page 5

> Provide a summary of what this visualization shows and how it helps to answer your research question.   

* * *

# References

*Include any references that you might have used to construct your graphic. This may include, but is not limited to citations for: graphics used, coding techniques, data collection, R-Markdown/RStudio documentation, etc. Delete this when complete.*

1. Reference 1
2. Reference 2
3. Reference 3
4. Reference 4
5. Reference 5

* * *

## All done!

Knit the completed R Markdown file as a HTML document (click the "Knit" button at the top of the script editor window) and upload it to the submission portal on Canvas.